\documentclass[10pt]{extarticle}
\title{}
\author{Avinash Iyer}
\date{}
\usepackage[shortlabels]{enumitem}

%font setup
%
%\usepackage[math]{anttor}

%paper setup
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=1in}
\usepackage{fancyhdr}

%symbols
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{gensymb}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

%chemistry stuff
\usepackage[version=4]{mhchem}
\usepackage{chemfig}

%plotting
\usepackage{pgfplots}
\usepackage{tikz}

%\usepackage{natbib}

%graphics stuff
\usepackage{graphicx}
\graphicspath{ {./images/} }

%code stuff
%when using minted, make sure to add the -shell-escape flag
%you can use lstlisting if you don't want to use minted
%\usepackage{minted}
%\usemintedstyle{pastie}
%\newminted[javacode]{java}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}
%\newminted[cppcode]{cpp}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
	language=Java,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}
% text + color boxes
\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\newtcolorbox{problem}[1]{colback = white, title = {#1}, breakable}
\newtcolorbox{solution}{colback = white, colframe = black!75!white, breakable, title = Solution}
%including PDFs
\usepackage{pdfpages}
\setlength{\parindent}{0pt}

\pagestyle{fancy}
\fancyhf{}
\rhead{Avinash Iyer}
\lhead{Problem Set 5}
\begin{document}
  \begin{problem}{An Increase in Research Productivity}
    Suppose that the economy is on a balanced growth path in the Romer model. Then, in $2030$, research productivity $\overline{z}$ rises immediately and permanently to $\overline{z}'$.
    \begin{enumerate}[(a)]
      \item Make a graph of $y_t$ over time using a ratio scale.
      \item Why might research productivity increase in an economy?
    \end{enumerate}
  \end{problem}
  \begin{solution}
    \begin{tcolorbox}[colback = white, title = (a), breakable]
      \begin{center}
        \begin{tikzpicture}[scale = 0.75]
          \draw[thin, gray] (0,0) grid (10,10);
          \draw[thick, black] (0,0) -- (0,10);
          \draw[thick, black] (0,0) -- (10,0);
          \draw[blue] (0,0) -- (4,4);
          \draw[blue] (4,4) -- (6,10);
          \draw [thick, red,dashed] (4,4) -- (4,0);
          \node [anchor = south] at (5,10) {Output over Time, ratio scale};
          \node [anchor = north] at (4,0) {$2030$};
          \node[anchor = east] at (0,1) {$1$};
          \node[anchor = east] at (0,2) {$2$};
          \node[anchor = east] at (0,3) {$4$};
          \node[anchor = east] at (0,4) {$8$};
          \node[anchor = east] at (0,5) {$16$};
          \node[anchor = east] at (0,6) {$32$};
          \node[anchor = east] at (0,7) {$64$};
          \node[anchor = east] at (0,8) {$128$};
          \node[anchor = east] at (0,9) {$256$};
          \node[anchor = east] at (0,10) {$512$};
          \node[anchor = south, rotate = 90] at (-0.5,5) {Output};
          \node[anchor = north] at (5,-0.5) {Time};
        \end{tikzpicture}
      \end{center}      
    \end{tcolorbox}
    \begin{tcolorbox}[colback = white, title = (b), breakable]
      Research productivity might increase in an economy if the government undertakes large scale investments in education or increases the prizes or patents that it provides to new research that entices different types of innovations.
    \end{tcolorbox}
  \end{solution}
  \begin{problem}{Numbers in the Romer Model}
    Suppose the parameters in the Romer model are as follows: $\overline{A}_0 = 100$, $\overline{\ell} = 0.1$, $\overline{z} = 1/500$, and $\overline{L} = 100$.
    \begin{enumerate}[(a)]
      \item What is the growth rate of output per person in this economy?
      \item What is the initial level of output per person? What is the level of output per person after 100 years?
      \item Suppose research share were to double. How would you answer parts (a) and (b)?
    \end{enumerate}
  \end{problem}
  \begin{solution}
    \begin{tcolorbox}[colback = white, title = (a), breakable]
      The growth rate of output is equal to the growth rate of $A$, which is equal to:
      \begin{align*}
        g_a &= \overline{z}\overline{\ell}\overline{L} \\
            &= \boxed{0.02}
      \end{align*}
    \end{tcolorbox}
    \begin{tcolorbox}[colback = white, title = (b), breakable]
      The initial level of output per person is equal to:
      \begin{align*}
        y_0 &= \overline{A}_0 (1-\overline{\ell})\\
            &= \boxed{90}\\ 
            \\
        y_{100} &= \overline{A}_0 (1-\overline{\ell})(1 + \overline{z}\overline{\ell}\overline{L})^{100}\\
                &= \boxed{652}
      \end{align*}
    \end{tcolorbox}
    \begin{tcolorbox}[colback = white, title = (c), breakable]
      If research share were to double, we would get the following results:
      \begin{align*}
        g_a &= \overline{z}\overline{\ell}\overline{L}\\
            &= 0.04 \\
            \\
        y_0 &= \overline{A}_0 (1-\overline{\ell}) \\
            &= 80 \\
            \\
        y_{100} &= \overline{A}_0 (1-\overline{\ell})(1 + \overline{z}\overline{\ell}{\overline{L}})^{100} \\
                &= 4041
      \end{align*}
    \end{tcolorbox}
  \end{solution}
  \begin{problem}{A Variation of the Romer Model}
    Consider the following variation:
    \begin{align*}
      Y_t = A_t^{1/2}L_{yt}\\
      \Delta A_t = \overline{z}A_tL_{at}\\
      L_{yt} + L_{at} = \overline{L}\\
      L_{at} = \overline{\ell}\overline{L}
    \end{align*}
    There is only a single difference: we have changed the exponent on $A_t$ in the production of the output good so there is now a diminishing product to new ideas in that sector.
    \begin{enumerate}[(a)]
      \item Provide an economic interpretation for each equation.
      \item What is the growth rate of knowledge in this economy?
      \item Solve for the level of output per person at each point in time.
      \item What is the growth rate of output per person in this economy?
    \end{enumerate}
  \end{problem}
  \begin{solution}
    \begin{tcolorbox}[colback = white, title = (a), breakable]
      \begin{itemize}
        \item In the first equation, we are assuming that output is a function of ideas, $A$, which have diminishing marginal product, and labor output.
        \item In the second equation, the rate of new idea production is equal to the product of $\overline{z}$, the research productivity, and $L_{at}$, the labor force dedicated to research output, as well as the previous year's research (since we are assuming no ``idea depreciation'').
        \item In the third equation, we have our resource constraint --- namely, that there is a finite number of laborers, split between labor output and research output.
        \item In the fourth equation, we are defining the research labor to be a certain fraction, $\overline{\ell}$ of the total labor force $\overline{L}$.
      \end{itemize}
    \end{tcolorbox}
    \begin{tcolorbox}[colback = white, title = (b), breakable]
      \begin{align*}
        \Delta A_t &= \overline{z}\overline{\ell}\overline{L}A_t \\
        \frac{\Delta A_t}{A_t} &= \overline{z}\overline{\ell}\overline{L}\\
        \\
        g_a &= \boxed{\overline{z}\overline{\ell}\overline{L}}
      \end{align*}
    \end{tcolorbox}
    \begin{tcolorbox}[colback = white, title = (c) and (d), breakable]
      \begin{align*}
        Y_t &= A_t^{1/2}L_{yt} \\
        y_t &= A_t^{1/2} (1-\overline{\ell}) \\
            &= A_0^{1/2} \left((1 + \overline{z}\overline{\ell}\overline{L})^t\right)^{1/2} (1-\overline{\ell}) \\
            &=  A_0^{1/2} (1 + \overline{z}\overline{\ell}\overline{L})^{t/2} (1-\overline{\ell}) \\
            \\
        g_y &= \frac{\overline{z}\overline{\ell}\overline{L}}{2}
      \end{align*}
    \end{tcolorbox}
  \end{solution}
  \begin{problem}{Methodologies Used by Macroeconomists to Conduct Research}
    How do the articles about development aid illustrate the various techniques used by economists to conduct research? Specifically, create a list of the various techniques that are discussed in these articles. Briefly, describe these techniques with concrete examples from the articles.
  \end{problem}
  \begin{solution}
    In ``Do conflicts cause poverty, or vice versa,'' the authors cite the technique of instrumental variables estimation to isolate the effects of conflicts vs. drought and other hardships, and found that poverty/drought does lead to conflicts. They also discuss typical correlations such as OLS.\\

    In the case of ``Incentives to learn,'' the authors looked at a randomized set of schools whose students were eligible to receive merit scholarships and tracked their academic performance as a result of cash incentives.\\

    Similarly, in ``Deciphering the Demand for Clean Water,'' the study authors used randomized trials to find the effects of different clean water interventions and the willingness to pay on the part of households.
  \end{solution}
  \begin{problem}{Development Aid}
    Development Aid. Based on the findings from the articles about development aid, how can development aid (1) reduce conflicts, (2) increase human capital attainment and (3) increase access to water.
  \end{problem}
  \begin{solution}
    \begin{enumerate}[(1)]
      \item Development aid can reduce conflicts by being used to alleviate droughts during periods of emergency.
      \item Development aid can increase human capital attainment by providing incentives to students to increase their education levels.
      \item Development aid can increase access to water by funding water treatment and other measures to remove contaminants.
    \end{enumerate}
  \end{solution}
\end{document}
