---
title: "R Workthrough"
output: html_document
author: Avinash Iyer
permalink: "/NSP_R_Workthrough"
---
## First Steps
To store a vector to a variable, we do the following:
```{r}
x <- c(1,2,4)
```
We can also store this variable into a new variable:
```{r}
q <- c(x,x,8)
```
Then, we print `q`:
```{r}
q
```
To pull out the individual element, we do the following:
```{r}
x[3]
```
Elements of vectors in R are indexed at 1, **not** 0. For example, we would get an error if we tried to find `x[0]`. Importantly, we can also do subsets (or slicing, if we're talking about Python syntax).
```{r}
x[2:3]
```
The syntax `x[2:3]` means we start at index 2 (or the 2nd element) and go until (and including) index 3 (or the 3rd element). For example, with our vector `q`:
```{r}
q[2:4]
```
We can also find some values:
```{r}
mean(x)
sd(x)
```
R also has a bunch of internal data sets that we can use for our own edification by typing in the following:
```{r message=FALSE}
data()
```
For example, we can use the dataset `Nile` for some fun:
```{r}
mean(Nile)
sd(Nile)
hist(Nile)
```