---
title: "R Workthrough"
author: "Avinash Iyer"
permalink: /NSP_R_Workthrough
output: 
  html_document:
    keep_md: true
---

## Getting Started

To store a vector to a variable, we do the following:

```{r}
x <- c(1,2,4)
```

We can also store this variable into a new variable:

```{r}
q <- c(x,x,8)
```

Then, we print `q`:

```{r}
q
```

To pull out the individual element, we do the following:

```{r}
x[3]
```

Elements of vectors in R are indexed at 1, **not** 0. For example, we would get an error if we tried to find `x[0]`. Importantly, we can also do subsets (or slicing, if we're talking about Python syntax).

```{r}
x[2:3]
```

The syntax `x[2:3]` means we start at index 2 (or the 2nd element) and go until (and including) index 3 (or the 3rd element). For example, with our vector `q`:

```{r}
q[2:4]
```

We can also find some values:

```{r}
mean(x)
sd(x)
```

R also has a bunch of internal data sets that we can use for our own edification by typing in the following:

```{r message=FALSE}
data()
```

For example, we can use the dataset `Nile` for some fun:

```{r}
mean(Nile)
sd(Nile)
hist(Nile)
```

To make a function, we can define as follows:

```{r}
oddcount <- function(x){
  k<- 0 # assign 0 to k
  for (n in x){
    if(n%% 2 == 1) k<-k+1 # %% is modulus
  }
  return(k)
}
```

We can test our `oddcount` function on various vectors:

```{r}
oddcount(c(1,3,5))
oddcount(c(1,3,7,9,2,4))
```

In function `oddcount`, the values of `k` and `n` are local variables, and so don't really exist until the function is called. This is different from Python. Additionally, functions are passed by value rather than by reference. Let's create a function called `addone`, and see what happens to our vectors.

```{r}
addone <- function(x){
  for(i in 1:length(x)){
    x[i] <- x[i]+1
  }
  return(x)
}
z <- c(1,3,5)
addone(z)
z
```

## Vectors
In R, there is no separate thing as a "scalar," since scalars are considered to be 1-dimensional vectors. We define vectors as follows:
```{r}
x <- c(1,3,4)
x
length(x)
```
R automatically recycles (or basically copypastes) the shorter vector in addition until it reaches the length of the longer vector, as follows:
```{r}
y<- c(1,3,4,5,6)
y
z <- x+y
z
```
This is equivalent to adding `c(1,3,4,1,3)` to `c(1,3,4,5,6)`.

Multiplication is performed elementwise:
```{r}
w <- c(1,3,4) * c(6,7,8)
w
```
This is true of other numeric operators:
```{r}
k <- w %% c(3,4,2)
k
```

Alternatively, we can do the following:
```{r}
w %% 2
```

We can also generate vectors with slicing operations:
```{r}
z <- 5:8
z
```

If we wanted to extract all but the last element, we can do either of the following:
```{r}
z[1:(length(z)-1)]
z[-length(z)]
```

Slicing is precedent over plus/minus, so be wary (which is why we put the `length(z)-1` in parentheses up there).

We can also make vectors from sequences as follows:
```{r}
seq(from=1.1,to=2,length=10)
```
Sequences help deal with the null vector problem:
```{r}
x <- c(5,12,13)
seq(x)
x <- NULL
seq(x)
```

We can also use the `rep(x,times)` function to repeat vectors a number of times.
```{r}
x <- rep(8,4)
x
```

We can also use the argument `each` within the `rep` function to change how numbers are repeated.
```{r}
rep(c(5,12,13),3)
rep(c(5,12,13),each=3)
```

We can also use the functions `any` and `all` as "or" or "and" for vector elements:
```{r}
x <- 1:10
any(x>8)
all(x>3)
any(x>88)
```

We can use the `any` and `all` functions to find the number of runs of 1s in a vector of 0s and 1s, as follows:
```{r}
findruns <- function(x,k){
  n <- length(x)
  runs <- NULL
  for(i in 1:(n-k+1)){
    if(all(x[i:(i+k-1)] == 1)){
      runs <- c(runs,i)
    }
  }
  return(runs)
}
findruns(c(1,1,0,0,1,1,1,0,1,1,1),2) # this function should return (1,5,6,9,10)
```

Considering that this function creates a new vector every time it finds a run, this is very memory inefficient. We can solve this by initializing a new vector in `runs` and then cutting it towards the end.
```{r}
findruns1 <- function(x,k){
  n <- length(x)
  runs <- vector(length=n) # create a vector of length n at the beginning
  count <- 0
  for(i in 1:(n-k+1)){
    if(all(x[i:(i+k-1)] == 1)){
      count <- count + 1 # remember that indexing in R starts at 1
      runs[count] <- i
    }
  }
  # this loop will change the vector elements in runs to the point where the runs start
  if(count > 0){ # if statement is to make sure we cut off our runs value
    runs <- runs[1:count]
  } else{
    runs <- NULL
  }
  return(runs)
}
findruns1(c(1,1,0,0,1,1,1,0,1,1,1),2)
```

Most operations can be vectorized, as in the following:
```{r}
u <- c(5,2,8)
v <- c(1,3,9)
u > v
```
Here, the function checks each element of the vectors `u` and `v`. Additionally, we could do the following:
```{r}
w <- function(x) return(x+1)
w(u)
```
Other standard functions are also vectorized:
```{r}
sqrt(u)
u+1
```
Additionally, they can be nested:
```{r}
sqrt(w(u))
round(sqrt(1:9))
```

Some functions end up working via vectorization even if they look like they have scalars. For example, the following function:
```{r}
add_square_vector <- function(x,c){
  return((x+c)^2)
}
```
We can do with a scalar element:
```{r}
add_square_vector(1:3,2)
```
Or even with a vector element:
```{r}
add_square_vector(1:3,1:3)
```

```{r include=FALSE}
library(knitr)
```

Imagine we have a vectorized function that yields a vector. For example:
```{r}
z12 <- function(z) return(c(z,z^2))
```
Then, we have the following:
```{r}
z12(3)
```
and
```{r}
z12(1:8)
```

In order to resolve this, we could use the `matrix` function:
```{r}
matrix(z12(1:8),ncol=2)
```
We can also use the `sapply(x,f)` (or *simplify apply*) to apply `f` to every element of `x` and convert to a matrix:
```{r}
sapply(1:8,z12)
```

To deal with `NA` values, we can illustrate using the following:
```{r}
x <- c(8,NA,12,168,13)
x
mean(x)
mean(x,na.rm=TRUE)
```
We use `na.rm` to remove `NA` values. Whereas `NA` does affect the `mean` and other mathematical functions, `NULL` does not:
```{r}
y <- c(8,NULL,12,168,13)
mean(y)
```